---
title: "HW3_Raines"
Author: Evgenii Raines
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
editor_options: 
  chunk_output_type: console
---

## Task


Create png file with synteny between ZANU and DONGOLA X, 2, and 3 chromosomes using the RIdeogram package.

## Solution

### Data import

First of all, let's import the dataset for both species and mapping info.

```{r warning=FALSE, include=FALSE}
# importing data.table package, which would be useful in the future
library("data.table")

# dongola data
dongola <- read.table(file = '~/Университет ИТМО/Учёба/Магистратура/Statistics 2/GitHub_Homeworks/Homeworks/Homeworks_done/HW3_Raines/DONGOLA_genes.tsv', sep = '\t', header = TRUE)

# zanu data
zanu <- read.table(file = '~/Университет ИТМО/Учёба/Магистратура/Statistics 2/GitHub_Homeworks/Homeworks/Homeworks_done/HW3_Raines/ZANU_genes.tsv', sep = '\t', header = TRUE)

# data for results of gene mapping between two species
map <- read.table(file = '~/Университет ИТМО/Учёба/Магистратура/Statistics 2/GitHub_Homeworks/Homeworks/Homeworks_done/HW3_Raines/gene_mapping.tsv', sep = '\t', header = TRUE)
```


## Creating templates for RIdeogram import

RIdeogram synteny plot requires 2 files: data about the sizes of chromosomes and synteny info. Let's start with the first one.

1. The length for the ZANU's chromosomes we know from the task file

X: 27238055
2: 114783175
3: 97973315

2. The length for the DONGOLAS's chromosomes can be found in the [original publication](https://academic.oup.com/gigascience/article/10/3/giab017/6170950?login=true)

X: 26913133 
2: 111988354
3: 95710210

And know we can make the karyotype file.

```{r}
# create table for karyotype

karyotype_dual_comparison = data.table(
  Chr = c("X","2","3","X","2","3"),
  Start = 1,
  End = c("27238055", "114783175", "97973315", "26913133", "111988354", "95710210"),
  fill = 969696,
  species = c("ZANU", "ZANU", "ZANU", "DONGOLA", "DONGOLA", "DONGOLA"),
  size = 12,
  color = 252525
)
```


```{r}
# the table

karyotype_dual_comparison
```

And then, create a template for the future synteny table.

```{r}

```

